\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-04 grassposter/2015_EGU_Python/main.tex
python poster: blocks for outline, bash in documentation to python block, generated interface block, width according to other EGU posters
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64799 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[innermargin=10mm]{tikzposter}
\usepackage{enumitem}
\geometry{paperwidth=63in,paperheight=42in}
\usepackage{url}

\title{
  \begin{minipage}{\textwidth}
    \centering
    Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
  \end{minipage}
}
\author{
V\'{a}clav Petr\'{a}\v{s} (1), Anna Petr\'{a}\v{s}ov\'{a} (1), Yann Chemin (2), Pietro Zambelli (3), Martin Landa (4), \\
S\"{o}ren Gebbert (5), Markus Neteler (6), and Peter L\"{o}we (7)
}
\institute{
\large  % using smaller size of font than default because the list is long
(1) North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu), (2) International Water Management Institute,
Pelawatta, Sri Lanka, (3) EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy, (4) Faculty of Civil
Engineering, Czech Technical University in Prague, Czech Republic, (5) Th\"{u}nen Institute of Climate-Smart Agriculture,
Braunschweig, Germany, (6) Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy, (7)
German National Library for Science and Technology, Hanover, Germany
}
% \titlegraphic{}

@@

@@

\makeatletter
\renewcommand\TP@maketitle{%
    \begin{minipage}{0.2\linewidth}
       \centering

       % TODO: get other logos
       \includegraphics[width=0.2\textwidth]{ncstate}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{iwmi}

       \vspace{4ex}

       \includegraphics[width=0.2\textwidth]{ncstate}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ctu_prague}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ncstate}

       \vspace{4ex}

       \includegraphics[width=0.2\textwidth]{fem_cri}
       \hspace{2ex}
       \includegraphics[width=0.2\textwidth]{ncstate}
    \end{minipage}%
    \hfill
   \begin{minipage}{0.6\linewidth}
        \centering
        \color{titlefgcolor}
        {\bfseries  \sc {\fontsize{85}{60}\selectfont \@title}  \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.2\linewidth}
       \centering
       \includegraphics[width=0.39\textwidth]{grass}\\
       \LARGE \textbf{\textsf{GRASS GIS}}
    \end{minipage}
}
\setlength{\TP@visibletextwidth}{\textwidth-3\TP@innermargin}
\setlength{\TP@visibletextheight}{\textheight-3\TP@innermargin}

@@

@@

\newcommand{\gmodule}[1]{\emph{#1}}
\newcommand{\rafun}[1]{\texttt{#1()}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Highlights}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS is a platform for geospatial computations.
\item The framework supports code maintenance which results in long term preservation of algorithms.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Description}{
% \textfontsize
\Large
\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
% \setlength{\parskip}{1em}

@@

\block{Example of including code generated aside}{

% listings package does not work well with the tikzposter class,
% so we need to include pdf
\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{sample}

@@

\block{Sample block}{
\textfontsize

See abstact for topics which can become blocks.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Acknowledgements}{
\begin{tabular}{cp{28em}}
\raisebox{-.4\height}{
\includegraphics[width=0.2\linewidth]{osgeo}
}
& GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\\
\raisebox{-.8\height}{
\includegraphics[width=0.2\linewidth]{google}
}
& Initial development of pygrass and gunittest packages was done during Google Summer of Code.
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{References}{

>>>>

\documentclass[innermargin=10mm]{tikzposter}
\usepackage{enumitem}
\geometry{paperwidth=197cm,paperheight=100cm}
\usepackage{url}

\usepackage{alltt}

\newcommand{\inst}[1]{\hspace{2pt}$^{\mbox{\normalsize#1}}$\hspace{-7pt}}
\newcommand{\instlist}[1]{\hspace{1pt}$^{#1}$}

\title{
  \begin{minipage}{\textwidth}
    \centering
    Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7
    \bigskip
  \end{minipage}
}
\author{
V\'{a}clav Petr\'{a}\v{s}\inst{1},
Anna Petr\'{a}\v{s}ov\'{a}\inst{1},
Yann Chemin\inst{2},
Pietro Zambelli\inst{3},
Martin Landa\inst{4},
S\"{o}ren Gebbert\inst{5},
Markus Neteler\inst{6}, and
Peter L\"{o}we\inst{7}
}
\institute{
\large
\instlist{1}North Carolina State University, Raleigh, USA (wenzeslaus@gmail.com, vpetras@ncsu.edu),
\instlist{2}International Water Management Institute, Pelawatta, Sri Lanka,
\instlist{3}EURAC Research, Institute for Renewable Energy, Bolzano/Bozen, Italy,
\instlist{4}Faculty of Civil Engineering, Czech Technical University in Prague, Czech Republic,
\instlist{5}Th\"{u}nen Institute of Climate-Smart Agriculture, Braunschweig, Germany,
\instlist{6}Research and Innovation Centre, Fondazione Edmund Mach, San Michele all'Adige, Italy,
\instlist{7}German National Library for Science and Technology, Hanover, Germany
}
% \titlegraphic{}

@@

\definecolor{titleTextColor}{HTML}{2E652E}

@@

\makeatletter
\renewcommand\TP@maketitle{%
    \begin{minipage}{0.12\linewidth}
       \centering

       \newcommand{\logowidth}{0.17\textwidth}
       \newcommand{\logovspace}{\vspace{3ex}}
       \newcommand{\logohspace}{\hspace{1ex}}

       % TODO: get other logos
       \includegraphics[width=\logowidth]{ncstate}
       \logohspace
       \includegraphics[width=\logowidth]{iwmi}

       \logovspace

       \includegraphics[width=\logowidth]{ncstate}
       \logohspace
       \includegraphics[width=\logowidth]{ctu_prague}
       \logohspace
       \includegraphics[width=\logowidth]{ncstate}

       \logovspace

       \includegraphics[width=\logowidth]{fem_cri}
       \logohspace
       \includegraphics[width=\logowidth]{ncstate}
    \end{minipage}%
    \hfill
   \begin{minipage}{0.74\linewidth}
        \centering
        \color{titlefgcolor}
        {\textcolor{titleTextColor}{\textsf{\textbf{{\fontsize{85}{60}\selectfont \@title}}}}  \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.12\linewidth}
       \centering
       \includegraphics[width=0.35\textwidth]{grass}\\
       \Large \textbf{\textsf{GRASS GIS}}
    \end{minipage}
}
\setlength{\TP@visibletextwidth}{\textwidth-3\TP@innermargin}
\setlength{\TP@visibletextheight}{\textheight-3\TP@innermargin}

@@

% listings package does not work well with the tikzposter class,
% so we need to include PDFs with code generated separately

@@

% GRASS module
\newcommand{\gmodule}[1]{\emph{#1}}

\newcommand{\rafun}[1]{\texttt{#1()}}

% GRASS Python package
\newcommand{\pkg}[1]{\emph{#1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Highlights}{
% \setlength{\parskip}{1em}
\textfontsize
% \begin{itemize}
\renewcommand{\item}{\par\vspace{0.8ex}}
\item GRASS GIS is a platform for geospatial computations.
\item The framework supports code maintenance which results in long term preservation of algorithms.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Description}{
% \textfontsize
\Large
\newcommand{\intropartitle}[1]{\parinlinetitle{#1}}
% \setlength{\parskip}{1em}

@@

\block{GRASS Scripting library interface to GRASS GIS modules}{

The same applies to \pkg{grass.pygrass} syntax:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{PyGRASS interface to GRASS GIS modules}{

The same applies to \pkg{grass.pygrass} syntax:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using documentation for GRASS GIS modules}{

Documentation of GRASS GIS modules usually use Bash syntax for examples:

\begin{alltt}
r.neighbors input=elevation output=elevation\_smooth method=median -c
\end{alltt}

This can be easily rewritten to \pkg{grass.script} syntax:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}

The same applies to \pkg{grass.script} syntax:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\pkg{ctypes} interface to C libraries}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using NumPy}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Using IPython Notebook}{

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Automatic creation of GUI and CLI}{

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{grass_module}

\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_gui}
\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{grass_module_cli}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{PyGRASS interface to C libraries}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Python script versus GRASS GIS module}{
and running code from IDE
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Temporal framework}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Testing the code}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{GRASS GIS Addons}{
The GRASS GIS Addons ensures long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS itself.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Alternatives to Python}{
GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
and as subprocesses virtually any language as long as proper environment is set.

The GRASS GIS library has a C API which is often used to create GRASS modules in C and C++.

GRASS GIS modules can be used in R using \pkg{rgrass7} package.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{Acknowledgements}{
\begin{tabular}{cp{0.75\linewidth}}
\raisebox{-.4\height}{
\includegraphics[width=0.2\linewidth]{osgeo}
}
& GRASS GIS is a OSGeo project. OSGeo provides infrastructure for websites and source code management.
\\
\raisebox{-.8\height}{
\includegraphics[width=0.2\linewidth]{google}
}
& Initial development of \pkg{pygrass} and \pkg{gunittest} packages was done during Google Summer of Code.
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{References}{
